---
title: "Week 13 Activity"
author: "CONGQI MIAO"
date: "April 17, 2022"
output: html_notebook
---

```{r}
library(tidyverse)
Data_RegEx3.csv <- read.csv("Data_RegEx3.csv")
df <- Data_RegEx3.csv
```


### Create New variable year Based on First Four Digits of tourny_id
```{r}
df <- df %>% mutate(year = substr(tourney_id, 1, 4))
head(df,3)
tail(df,3)
```

### Separate ‘score’ variable into 5 columns based on ‘score’ results
```{r}
df <- df %>% 
  mutate(Set = gsub(" *\\(.*?\\) *", "", score)) %>%
  separate(Set, into=c("Set.1", "Set.2", "Set.3", "Set.4", "Set.5"), sep= " ")
head(df,3)
tail(df,3)
```

### Create new variable ’sets.played’by counting non-NAs in Set.1 through Set.5
```{r}
df <- df %>%  
  mutate(setsplayed = factor(rowSums(!is.na(df[8:12])))) %>%
  select(!c("Set.1", "Set.2", "Set.3", "Set.4", "Set.5"))
head(df,3)
tail(df,3)
```

### Create Density Plot of Minutes Played by Number of Sets Played
```{r}
ggplot(df, aes(minutes, fill = setsplayed, color = setsplayed)) +
  geom_density() +
  theme(legend.position = "top") +
  labs(title = "Density Plots of Minutes Played Per Number of Sets Played",
       x = "Minutes Played", y = "Density")

```

### Create Boxplot of Winner’s Age by Tournament Name
```{r}
df[df$tourney_name == "Us Open",]$tourney_name = "US Open"

ggplot(df, 
       aes(tourney_name, winner_age, color = tourney_name)) +
  geom_boxplot() +
  labs(title = " Boxplot Age of Winner in Grand Slam Events",
       x = "Tournament Name", "Age of Winner",
       color = "Tournament Name") 
```

### Counts of Matches Won by Top 5 IOC Membership per Tournament
```{r}
ggplot(df %>% group_by(tourney_name, winner_ioc) %>%
         summarise(total_won = n()) %>%
         top_n(n = 5, wt = total_won), 
       aes(winner_ioc, total_won)) +
  geom_point() +
  facet_grid(tourney_name~.) +
  theme_bw() +
  labs(title = "Top 5 Olympic Memberships per Tournament",
       x = "Winners Olympic Membership", y = "Tournaments Won")
```

### Counts of Matches Won by Top 2 IOC Membership per Year
```{r}
ggplot(df %>% group_by(year, winner_ioc) %>%
         summarise(total_won = n()) %>%
         top_n(n = 2, wt = total_won), 
       aes(year, total_won, color = winner_ioc)) +
  geom_point() +
  theme_bw() +
  labs(title = "Top 2 Olympic Memberships per Year",
       x = "Year", y = "Tournaments Won",
       color = "Olympic Memberships")

```

### GIthub pro https://github.com/CongqiMiao/STAT184-Activities.git